
\chapter*{Abstract}

The educational curriculum aims to ensure equal opportunities in the students' learning process by providing the necessary materials, resources, and content throughout their academic career. However, due to the diverse educational needs of students, sometimes curricular adaptations are necessary. Unfortunately, currently available tools for curricular adaptation mostly focus on specific types of adaptations. This means that teachers have to invest a significant amount of time in creating adapted academic materials for students who need them. They have to make textual adjustments, search for images, create exercises, and so on.

This project aims to provide a centralization of curricular adaptation tools. It involves the improvement and updating of a web application created in a Degree Final Proyect (DFP) during the 20/21 academic year, called AdaptaMaterialEscolar 1.0. It was specifically developed to simplify the process of non-significant curricular adaptation for teachers. We have redesigned the original application, improved some of the existing functionalities, and added new ones. The updated features in AdaptaMaterialEscolar include a pictogram search engine, fill-in-the-blank exercises, crossword puzzle generation, true or false questions, concept definitions, PDF export, and questions requiring developed answers within a limited space. Additionally, we have developed new features that expand the capabilities of the application. These include definition exercises, concept matching, integration of gapped mathematical formulas, a drawing space, color legend, summary generation, and a pictotranslator.

The web application AdaptaMaterialEscolar 2.0 has been evaluated by end-users who intend to use it during the school period. The obtained results demonstrate that the application meets a real need of teachers and show that its usability level is highly satisfactory.

The application can be accessed at \url{http://143.47.43.25/}, and the source code can be found at \url{https://github.com/NILGroup/TFG-22-23-AdaptaMaterialEscolar2.0}.


\section*{KeyWords}

Non-significant curricular adaptation

Accessibility

Teaching tool

Text editor

Web application

Academic material

Special educational needs

Educational technology

Educational innovation


